Deep Probabilistic Models for Camera Geo-Calibration

### 2018-09-06 chapters/introduction/introduction.tex
Apply Natha (writing center)'s review opinions.

Manually engineering visual features is a common practice for
computer vision tasks. One of the successful example of manual
feature is SIFT~\cite{lowe1999object}, which is widely used by many
computer vision algorithms.
In recent years, automatic feature engineering has drawn more
attentions. Compared to the manual feature
engineering, automatic feature engineering approaches allow to learn
useful features without strong expert knowledge about the data. Among
these learning approaches, deep neural networks are intensively studied.
The most common approach for deep feature learning is full
supervision, which usually requires large number of manual
annotations~\cite{yosinski2014transferable,zhou2016learning,wen2016discriminative}.
Unfortunately, such data is not always available for certain tasks or
needs to invest a huge amount of human labors to create.  In contrast,
unlabeled data is often plentiful (\ie cellphone photos in Instagram
or Youtube videos).

To exploit these unlabeled data, recent work has explored
self-supervision methods (sometimes referred to as unsupervised learning or
pretext tasks) for training deep neural networks that capture useful
visual representations~\cite{doersch2015unsupervised,pathak2016context}. 
These methods typically
exploit some known quantity of the data, like pixel color values, to
avoid expensive manual annotation.
By learning these quantities associated with the data, one
can obtain useful features of the image.
For example, Zhang et al.~\cite{zhang2016colorful} show how image
colorization (synthesizing colors for a grayscale image) is a powerful
pretext task for learning visual representations. Pathak et
al.~\cite{pathak2017learning} exploit low-level motion-based grouping
cues for unsupervised feature learning.  
%
As new learning technique that addresses the lack of massive amounts
of labeled data, domain adaptation forces the feature generating model
to adapt another feature domain so that it improves the performance
when dealing with new input
data~\cite{fernando2013unsupervised,fernando2015joint,saenko2010adapting,wang2016actions,tinghui2016flow}.
Duan \etal~\cite{duan2012learning} propose to learn a linear
projection to transfer from the source feature subspace to the target
subspace. Sohn \etal~\cite{sohn2017unsupervised} improve the
performance of video face recognition using an adversarial-based
approach to adapt the network to unlabeled video imagery.

@@

In this thesis, we make contributions in three main areas: 1) we
proposed a reflexible probabilistic model to jointly estimate the
geo-calibration parameters, 2) we decomposed the full geo-calibration
into several partial geo-calibration tasks, each of which provides a
strong constraint function that fits into the probabilistic model,
and 3) we show that learning to geo-calibrate a camera is a useful
pretext for image feature learning.

@@

\subsection{Flexible Probabilistic Model for Geo-Calibration}
We design a flexible probabilistic model to estimate the probability
over all geo-calibration parameters.
First, we construct a scoring function to model the process of camera
projecting the scene to image frame at given pose, location, and time.
%
The scoring function consists of a series of constraint functions,
which measures the ``fitness'' between these geo-calibration
parameters and the appearance of the image. 
%
The scoring function is proportional to the probability distribution
over the geo-calibration parameters. Since the integral over all
possible parameters is intractable, We propose a Markov Chain Monte
Carlo (MCMC) sampling approach to approximate the underlying
probability distribution. 
%
Our model is flexible that it allows different constraint functions
contribute to the scoring function. The details of this model can be
found in \chapref{mcmc}.

@@

\begin{itemize}[noitemsep]
  \item \textbf{Constraint for Camera Pose:}
  We build the constraint function for camera roll and pitch angles.
  Assuming the intrinsic parameters are known, camera roll and pitch
  angles can be derived from the horizon line position on the image.
  Compared to directly detecting the camera pose, identifying horizon
  line is easier because it can be explicitly estimated from the scene
  layout.
  In our work, we create a convolutional neural network to estimate the
  prior distribution over the horizon line.
  For each horizon line candidate sampled from the prior distribution,
  we assign a consistency score to it by measuring the consistencies of
  vanishing points detected on it.
  The constraint function output is defined as the multiplication of
  the prior probability of the associated horizon line and its
  consistency score.
  We present the algorithm details in \chapref{fasthorizon}.
  \newline

@@

\subsection{Geo-Calibration for Feature Learning and Image
Understanding}
Full supervision algorithms are powerful tools to learn useful image
features. However, full supervision algorithms require large number
of annotated data, which takes a lot of human labors and is usually
unavailable.
On the other hand, images with annotations like tags and GPS locations
uploaded by individual users or captured automatically by smart
devices are plentiful on the Internet.
To use these image resources to understand the world,
we explore two approaches that use time and
locations as weak annotations: 1) {\em ground-to-aerial segmentation}, and 2)
{\em geo-temporal feature learning} with time/location tagged images.

\begin{itemize}[noitemsep]
  \item \textbf{Ground-to-Aerial Segmentation:}
  Semantic segmentation plays an important role in image understanding.
  The training for semantic segmentation task requires a large number
  of annotated data.
  However, most large scale annotated datasets like ImageNet~\cite{ILSVRC15}
  and COCO~\cite{lin2014microsoft} are mostly made of ground-level
  images. By comparison, annotated datasets for aerial imagery are rare.
  %
  To deal with this problem, we proposed a
  DNN to learn semantic segmentation for aerial images with only
  ground-level annotations. Our method exploits the spatial
  correspondences between images in the cross-view pair, where the
  aerial imagery and ground imagery are associated by location and
  geo-orientation.
  In this work, we transfer the semantic knowledge from the
  ground domain to the aerial domain by identifying their latent
  geometric correspondences. Similar to {\em
  Reprojection Losses}~\cite{garg2016unsupervised,
  godard2017unsupervised,zhou2017unsupervised, yan2016perspective},
  which are proven to be successful in monocular depth estimation,
  our network learns the geometric projection from aerial to ground, and
  to semantically segment the aerial images jointly.
  We present the learning details in \chapref{crosstransf}
  \newline

>>>>

Manually engineering visual features is a common practice for
computer vision tasks. One of successful examples of manual
feature is SIFT~\cite{lowe1999object}, which is widely used by many
computer vision algorithms.
In recent years, automatic feature engineering has drawn more
attention. Compared to the manual feature
engineering, automatic feature engineering allows to learn
useful features with much less (if not none) knowledge about the data.
Among these learning approaches, deep neural networks are intensively
studied.  The most common approach for deep feature learning is full
supervision, which usually requires a large number of manual
annotations~\cite{yosinski2014transferable,zhou2016learning,wen2016discriminative}.
Unfortunately, such data is not always available for certain tasks or
requires a huge amount of human labor. 
In contrast, unlabeled data is often plentiful (\ie cellphone photos in Instagram
or Youtube videos).

To lavage these unlabeled data, recent work has explored
self-supervision methods (sometimes referred to as unsupervised learning or
pretext tasks) for training deep neural networks that capture useful
visual representations~\cite{doersch2015unsupervised,pathak2016context}. 
These methods typically
exploit some known quantity of the data, like pixel color values, to
avoid expensive manual annotation.
By learning these quantities associated with the data, one
can obtain useful features of the image.
For example, Zhang et al.~\cite{zhang2016colorful} show how
synthesizing colors for a grayscale image is a powerful
pretext task for learning visual representations. Pathak et
al.~\cite{pathak2017learning} exploit low-level motion-based grouping
cues for unsupervised feature learning.  
%
As one of new learning techniques that address the lack of massive amounts
of labeled data, domain adaptation forces the feature generating model
to adapt another feature domain so that it improves the performance
when dealing with new input
data~\cite{fernando2013unsupervised,fernando2015joint,saenko2010adapting,wang2016actions,tinghui2016flow}.
Duan \etal~\cite{duan2012learning} propose to learn a linear
projection to transfer from the source feature subspace to the target
subspace. Sohn \etal~\cite{sohn2017unsupervised} improve the
performance of video face recognition using an adversarial-based
approach to adapt the network to unlabeled video imagery.

@@

We make contributions in three main areas: 1) we
proposed a reflexible probabilistic model to jointly estimate the
geo-calibration parameters, 2) we decomposed the full geo-calibration
into several partial geo-calibration tasks, each of which provides a
strong constraint function that fits into the probabilistic model,
and 3) we show that learning to geo-calibrate a camera is a useful
pretext for image feature learning.

@@

\subsection{Flexible Probabilistic Model for Geo-Calibration}
We design a flexible probabilistic model to estimate the probability
over all geo-calibration parameters.
First, we construct a scoring function to model the process of camera
projecting the scene to image frame at given pose, location, and time.
%
The scoring function measures the ``fitness'' between these
geo-calibration parameters and the appearance of the image. 
It consists of a series of constraint functions,
%
The scoring function is proportional to the probability distribution
over the geo-calibration parameters. Since the integral over all
possible parameters is intractable, we propose a Markov Chain Monte
Carlo (MCMC) sampling approach to approximate the underlying
probability distribution. 
%
Our model is flexible because it allows different constraint functions
contribute to the scoring function. The details of this model can be
found in \chapref{mcmc}.

@@

\begin{itemize}[noitemsep]
  \item \textbf{Constraint for Camera Pose:}
  We build the constraint function for camera roll and pitch angles.
  Assuming the intrinsic parameters are known, camera roll and pitch
  angles can be derived from the horizon line position on the image.
  Compared to directly detecting the camera pose, identifying the horizon
  line is easier because it can be explicitly estimated from the scene
  layout.
  In our work, we create a convolutional neural network to estimate the
  prior distribution over the horizon line.
  For each horizon line candidate sampled from the prior distribution,
  we assign a consistency score to it by measuring the consistencies of
  vanishing points detected on it.
  The constraint function output is defined as the multiplication of
  the prior probability of the associated horizon line and its
  consistency score.
  We present the algorithm details in \chapref{fasthorizon}.
  \newline

@@

\subsection{Geo-Calibration for Feature Learning and Image
Understanding}
Full supervision algorithms are powerful tools to learn useful image
features. However, full supervision algorithms require large number
of annotated data, which takes a lot of human labor and is usually
unavailable.
On the other hand, images with annotations like tags and GPS locations
uploaded by individual users or captured automatically by smart
devices are plentiful on the Internet.
To use these image resources to understand the world,
we explore two approaches that use time and
locations as weak annotations: 1) {\em ground-to-aerial segmentation}, and 2)
{\em geo-temporal feature learning} with time/location tagged images.

\begin{itemize}[noitemsep]
  \item \textbf{Ground-to-Aerial Segmentation:}
  Semantic segmentation plays an important role in image understanding.
  The training for semantic segmentation tasks require a large number
  of annotated data.
  However, most large scale annotated datasets like ImageNet~\cite{ILSVRC15}
  and COCO~\cite{lin2014microsoft} are mostly made of ground-level
  images. By comparison, annotated datasets for aerial imagery are rare.
  %
  To deal with this problem, we proposed a
  DNN to learn semantic segmentation for aerial images with only
  ground-level annotations. Our method exploits the spatial
  correspondences between images in the cross-view pair, where the
  aerial imagery and ground imagery are associated by location and
  geo-orientation.
  In this work, we transfer the semantic knowledge from the
  ground domain to the aerial domain by identifying their latent
  geometric correspondences. Similar to {\em
  Reprojection Losses}~\cite{garg2016unsupervised,
  godard2017unsupervised,zhou2017unsupervised, yan2016perspective},
  which are proven to be successful in monocular depth estimation,
  our network learns the geometric projection from aerial to ground, and
  to semantically segment the aerial images jointly.
  We present the learning details in \chapref{crosstransf}
  \newline
